%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Change the font size of your document - 10pt, 12.1pt, etc.
\documentclass[letterpaper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\setstretch{1.25}
\usepackage{hyperref}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{bleudefrance}{rgb}{0.19,0.55,0.91}
\definecolor{gunmetal}{rgb}{0.16,0.2,0.22}
\hypersetup{
  colorlinks=true,
  % urlcolor={blue},
  % linkcolor={blue}
  urlcolor={bleudefrance},
  linkcolor={bleudefrance}
}

\usepackage{changepage}

\usepackage{hanging}

\usepackage{graphicx}
\graphicspath{ {images/}} %upload your signature to this file
%Change the margins to fit your CV/resume content
\usepackage[left=1in, right=1in, bottom=1.25in, top=1.25in]{geometry}

%Skype information - include your Skype name for a link to add you on Skype
% \newcommand*{\Skype}{\href{skype:john.smith?add}{john.smith}} 
% \newcommand{\Absender}[1][\normalsize]{\Skype} 

%Changes the page numbers - {arabic}=arabic numerals, {gobble}=no page numbers, {roman}=Roman numerals
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%% NAME OF APPLICANT %%%%%%%%%%%%%%%%%%%

\noindent  \textcolor{gunmetal}{\LARGE{\textbf{Matthew Adam Turner}}} \\
\vspace{-2ex}
\hrule 
\normalsize

%%%%%%%%%%%%%%%%% CONTACT INFORMATION %%%%%%%%%%%%%%%%%
% Your email address, website, and Skype name are links to send email, open your website and add you on Skype. 

\begin{center}
\begin{tabular}{l l}
 University of California, Merced & \hspace{1in} \href{mailto:mturner8@ucmerced.edu}{mturner8@ucmerced.edu} \\
 Cognitive and Information Sciences    & \hspace{1in}  \href{http://mt.digital}{mt.digital}   \\
  5200 Lake Road             & \hspace{1in} GitHub: \href{https://github.com/mt-digital}{mt-digital}  \\
 Merced, CA, 95348 & \hspace{1in} Phone: +1 (585) 350-8649 \\
\end{tabular}
\end{center}

% \vspace{1em}

%%%%%%%%%%%%%%%%% MAIN BODY %%%%%%%%%%%%%%%%%%%%%%%%%%%
% The main body is contained in a tabular environment. To move sections onto the next page, simply end the tabular environment and begin a new tabular environment.
\section*{\textcolor{gunmetal}{Education}}

% \begin{minipage}{0.9\textwidth}
  \begin{hangparas}{0.25in}{1}

    \textbf{Ph.D. candidate}, Cognitive and Information 
      Sciences, \emph{University of California, Merced}. Expected Summer 2021. Adviser: Paul E. Smaldino; Committee:
    Christopher T. Kello, Teenie Matlock, and Jeffrey Yoshimi.

    \textbf{M.S. with thesis}, Applied Physics, \emph{Rice University}, 2012. Adviser: 
      Kevin F. Kelly.

    \textbf{B.S.} Mathematics, Physics. \emph{Syracuse University}, 2008.
  \end{hangparas}

\noindent
% \textcolor{gunmetal}{{\Large Professional experience}} \\
% \subsection*{\textcolor{gunmetal}{Professional experience}}
\section*{\textcolor{gunmetal}{Professional experience}}

% \begin{minipage}{0.9\textwidth}
  \begin{hangparas}{0.25in}{1}
    2014 - 2016 \hspace{-0.555em} \quad\textbf{Research Software Developer}, 
        \emph{Northwest Knowledge Network, University of Idaho}, Moscow, ID, USA. Led development of the ``Virtual Watershed'' modeling and data analysis \&
        management system and associated tools (see Volk \& Turner, 2019, and 
        Gregory, et al., 2020, listed below). 
        Integrated contributions of faculty, graduate students,
        and other professional software developers.

      2012 - 2014 \quad \textbf{Data Engineer}, 
      \emph{Economic Modeling Specialists Int'l}, Moscow, ID, USA.
      Ported legacy PHP code and SQL queries for large-scale 
      economic data processing
      and forecasting to the D programming language. 
      Developed novel approaches and applied best-practices to large-scale
      economic forecasts.

  \end{hangparas}
% \end{minipage}

\noindent
% {\Large Education} \\
% \subsection*{\textcolor{gunmetal}{Education}}
% \end{minipage} 

% Command for me as author (boldface).

\noindent
% {\Large Publications}  \\
\section*{\textcolor{gunmetal}{Publications}}
% \vspace{.1in}

% \begin{minipage}{0.9\textwidth}
\begin{hangparas}{0.25in}{1}
  \textbf{Turner MA} \& Smaldino PE. Is Group Polarization Real? A generative model of false group polarization detection. 
  \emph{In preparation}.

  \textbf{Turner MA} \& Smaldino PE. (2021). Mechanistic Modeling for the Masses - 
  commentary on Yarkoni, ``The generalizability crisis.''
  Behavioral and Brain Sciences. \url{https://psyarxiv.com/8pj9n}

  Smaldino PE \& \textbf{Turner MA}. (Accepted pending revisions) Covert Signaling is an Adaptive Communication Strategy in Diverse Populations. \emph{Psychological Review}.
  Preprint: \url{https://osf.io/preprints/socarxiv/j9wyn/}

  \textbf{Turner MA} \& Smaldino PE (2020). Stubborn Extremism as a Potential Pathway to Group Polarization. \emph{Proceedings of the 42$^{\,nd}$ Annual Conference of the Cognitive Science Society}. \url{https://cogsci.mindmodeling.org/2020/papers/0153/}

    Gregory A, \ldots, \textbf{Turner MA} (2020). Efficient Model-data Integration for Flexible Modeling, Parameter Analysis \& Visualization, and Data Management. \emph{Frontiers in Water}. 
    \url{https://doi.org/10.3389/frwa.2020.00002}

    Smaldino PE, \textbf{Turner MA}, Contreras Kallens PA (2019). Open Science and Modified Funding Lotteries Can Impede the Natural Selection of Bad Science. \emph{Royal Society Open Science}, 6(8), 191249. \url{https://doi.org/10.1098/rsos.191249}

    Volk JM \& \textbf{Turner MA} (2019). PRMS-Python: A Python framework for programmatic PRMS modeling and access to its data structures. \emph{Environmental Modelling and Software}, 114, 152–165. \url{https://doi.org/10.1016/j.envsoft.2019.01.006}

    \textbf{Turner MA} \& Smaldino PE (2018). Paths to Polarization: How Extreme Views,
    Miscommunication, and Random Chance Drive Opinion Dynamics. \emph{Complexity}. \url{https://doi.org/10.1155/2018/2740959}
    
  \textbf{Turner MA} (2012) \emph{Experimental and Numerical Investigations of Novel Architectures Applied to Compressive Imaging Systems}. Master's thesis. Rice University. Houston, Texas. (\href{https://www.researchgate.net/publication/274720620_Experimental_and_Numerical_In vestigations_of_Novel_Architectures_Applied_to_Compressive_Imaging_Systems}{link})

    Xu L, Davenport MA, \textbf{Turner MA}, Sun T, Kelly K (2011) Compressive Echelle Spectroscopy. \emph{Proceedings of the SPIE – The International Society for Optical Engineering.}

    Kanbur SM, Marconi M, Ngeow C, Musella I, \textbf{Turner MA}, et al. (2011) Period–colour and amplitude–colour relations in classical Cepheid variables – VI. New challenges for pulsation models. \emph{Monthly Notices of the Royal Astronomical Society}, 408 (2), 695-700.

    Kanbur SM, Marconi M, Ngeow C, Musella I, \textbf{Turner MA}, et al. (2009) Multiphase PC/PL Relations: Comparison Between Theory and Observations. AIP Conference Proceedings, Stellar Pulsations: Challenges for Theory and Observation, 1170 (September), 18-22.

    Acevedo R, Lombardini R, \textbf{Turner MA}, Kinsey JL, Johnson BR (2008)
    Quantum and electromagnetic propagation with the conjugate symmetric
    Lanczos method. \emph{Journal of Chemical Physics}, 128.
    
  \end{hangparas}
% \end{minipage} \\[.25in]

\noindent
% {\Large Preprints} \\
\section*{\textcolor{gunmetal}{Patent}}

% \begin{minipage}{0.9\textwidth}
  \begin{hangparas}{0.25in}{1}
  Kelly KF, Baraniuk RG, Woods G, Sun T, \textbf{Turner MA}. U.S. Patent No. 9,124,755. 
  ``Apparatus and method for compressive imaging and sensing through multiplexed modulation''.
  September 1, 2015.

    
  \end{hangparas}



\noindent
% {\Large Presentations} \\

\section*{\textcolor{gunmetal}{Presentations}}

% \begin{minipage}{0.9\textwidth}
  \begin{hangparas}{0.25in}{1}
    \textbf{Turner MA}, (2021, February) Statistical Models of Group Polarization: Putting Theory into Practice. Society for Personality and Social Psychology. Poster. Online.

    \textbf{Turner MA}, (2021, January) Social structure from repeated social interaction. Philosophy of Science Association. Poster. Online.

    \textbf{Turner MA} \& Smaldino PE, (2020, August) Group polarization via stubborn extremism. 42nd Annual Meeting of the Cognitive Science Society. Online. \href{https://www.researchgate.net/publication/342153646_Stubborn_extremism_as_a_potential_pathway_to_group_polarization}{Paper.} \href{https://youtu.be/i5PHjwu1p40}{Video.}

   \textbf{Turner MA} \& Smaldino PE, (2020, July) Group polarization via stubborn extremism. 6th International Conference on Computational Social Science. Online.

Kello C, \textbf{Turner MA}, Alviar C, (2019, August) A Statistical Model of Hierarchical Temporal Structure. The Guy Van Orden UConn Workshop on Cognition and Dynamics, XIV. Univeristy of Connecticut.

\textbf{Turner MA}, Bernacchi L, Maglio PP, Matlock T, (2018, December) How regulations strangle business: Lessons for science communication based on violence metaphors in the 2016 presidential election. eLightning talk at the American Geophysical Union meeting in Washington, D.C. \url{https://agu.confex.com/agu/fm18/meetingapp.cgi/Paper/451955}

\textbf{Turner MA} \& Smaldino PE, (2018, October) Cultural polarization depends on whom we learn from and how well we communicate. Lightning talk during plenary session presented at the Cultural Evolution Society meeting in Tempe, Arizona.

\textbf{Turner MA}, Maglio PP, Matlock, T, (2017, July) A corpus analysis of the dynamics of violence metaphors in cable news programming on US politics. Talk presented at the 14th International Cognitive Linguistics Conference in Tartu, Estonia.

\textbf{Turner MA}, Bernacchi, L, Maglio, PP, Matlock, T, (2017, June) Breaking news: the EPA is strangling the economy! An analysis of metaphorical violence and US environmental regulators. Talk presented at the 2017 Conference on Communication and the Environment.

\textbf{Turner MA}, Miller, SJ, Gregory, AE, Cadol, DD, Stone, MC, Sheneman, L, (2016, December). Coupled RipCAS-DFLOW (CoRD) Software and Data Management System for Reproducible Floodplain Vegetation Succession Modeling. Poster presented at the American Geophysical Society meeting in San Francisco, CA.

\textbf{Turner MA}, Koskela R, Vardigan M, Dubin D, Sheneman L. (2015, September). Linked Interdisciplinary Data Discovery. Poster presented at the 6th RDA Plenary in Paris, France. 
  \end{hangparas}
% \end{minipage} \\[.25in]


% \begin{minipage}{0.9\textwidth}
  % \begin{hangparas}{0.25in}{1}
  % \end{hangparas}
% \end{minipage} \\[.25in]

\noindent
\section*{\textcolor{gunmetal}{Awards}}
\begin{itemize}
  \item NSF Research Training (NRT) Program in Intelligent Adaptive Systems, September 2020 - August 2021.
  \item Research Data Alliance Early Career Fellow, May 2015
    (\href{https://rd-alliance.org/rda_us data share program}{info}).
  \item NSF Integrative Graduate Education and Research Traineeship (IGERT) Fellow, August 2010 - May 2012.
  \item NSF International Research Experience for Students (IRES) at UFSC,
    Santa Catarina, Brazil, Summer 2008;
    astrophysical research and autonomous telescope network development.
\end{itemize}

\noindent
\section*{\textcolor{gunmetal}{Teaching experience}}
\begin{itemize}
  \item Invited by Prof.\ Heather Bortfield to give lecture and workshop on cultural evolution and open science best-practices, Spring 2021
  \item Led hands-on workshop in Prof.\ Smaldino lab group on how to use the on-campus supercomputing cluster at UC Merced, Spring 2020
  \item TA/Computing lab instructor, Introduction to Artificial Intelligence, Prof.\ David Noelle, Fall 2017, 2018, \& 2019
  \item TA/Computing lab instructor and guest lecturer, Modeling Social Systems, Prof.\ Paul Smaldino, Spring 2019
  \item TA, Contemporary Moral Problems, Prof.\ David Jennings, Spring 2018
  \item TA, Introduction to Ethics, Prof.\ David Jennings, Spring 2017
  \item TA, Introduction to Cognitive Science, Prof.\ Rick Dale, Fall 2016
\end{itemize}

\noindent
\section*{\textcolor{gunmetal}{Mentorship}}
\begin{itemize}
  \item Mentored and supervised several UC Merced students in 2017 
    who contributed to
    Metacorps, the web application I developed for annotating metaphor found
    on cable news. Students were Gloria Quintana, Amy Tang, Sebastian Lavenant, Isabella Methot,
    Danny Zamora, and Conor Aaron.
  \item
    Mentored several graduate student programmers as part of the Virtual Watershed
    project with the Northwest Knowledge Network.
  \item Mentored and supervised undergraduate Joy Dai on a signal processing project using MATLAB for
    one semester of research at Rice University, 2011.
\end{itemize}

\noindent
\section*{\textcolor{gunmetal}{Preprints}}
\begin{hangparas}{0.25in}{1}

  \textbf{Turner MA}, Maglio PP, Matlock T (2018) Metaphorical Violence in Political Discourse. \url{https://doi.org/10.31235/osf.io/t8yg9}

  \textbf{Turner MA} (2018) A neural network to classify metaphorical violence on cable news. \url{https://arxiv.org/abs/1810.08677}

\end{hangparas}

\noindent
\section*{\textcolor{gunmetal}{Reviewer}}

  \begin{hangparas}{0.25in}{1}
    \emph{Psychological Review} $\cdot$ \emph{Cognitive Processing} $\cdot$ \emph{Cognitive Systems Research}
  \end{hangparas}


\noindent
\section*{\textcolor{gunmetal}{Skills}}

\begin{hangparas}{0.25in}{1}
  \textbf{Programming languages}: Python; R; NetLogo; bash/shell scripting; 
  HTML/CSS/JavaScript; Java; D; MATLAB; Mathematica; Clojure.

  \textbf{Technical proficiencies}: Agent-based modeling, computational 
  modeling; IPython and R notebooks; Cluster computing;
  Git/GitHub; Web servers; \LaTeX; MongoDB and SQL; REST APIs and API
  development.

  \textbf{Languages:} English; some experience with Portuguese, French,
  and Spanish.
\end{hangparas}


\end{document}

